SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-01 scipy-1.0/ckdtree.tex
Update scipy-1.0/ckdtree.tex
Co-Authored-By: tylerjereddy <tyler.je.reddy@gmail.com>

Specifically, in 2015, we enhanced \texttt{cKDTree.query} by reimplementing in C++,
removing some of the algorithm memory leaks, and allowing 
release of the GIL so that multiple threads may be used\cite{gh-4374}. In 2013,
the time complexity of the k nearest neighbor search from \texttt{cKDTree.query}
was approximately loglinear \cite{knn-jake}, and we've confirmed that this time
complexity has been preserved in SciPy \texttt{1.0.0} (Figure~\ref{fig:knn-complexity}),
but with generally improved efficiency (Figure~\ref{fig:asvbench}). The
discussion in the originally-cited nearest neighbor search
algorithm publication\cite{kdtree-search-algo}, suggests that there are
at least some scenarios where $O(log n)$ search time complexity may
be achieved, but the influence of dimensionality appears to be consistent
with our empirical observations of approximately $0(n log n)$ performance.

>>>>

Specifically, in 2015, we enhanced \texttt{cKDTree.query} by reimplementing in C++,
removing some of the algorithm memory leaks, and allowing 
release of the GIL so that multiple threads may be used\cite{gh-4374}. In 2013,
the time complexity of the k nearest neighbor search from \texttt{cKDTree.query}
was approximately loglinear \cite{knn-jake}, and we've confirmed that this time
complexity has been preserved in SciPy \texttt{1.0.0} (Figure~\ref{fig:knn-complexity}),
but with generally improved efficiency (Figure~\ref{fig:asvbench}). The
discussion in the originally-cited nearest neighbor search
algorithm publication\cite{kdtree-search-algo}, suggests that there are
at least some scenarios where $\mathcal{O}(\log{n})$ search time complexity may
be achieved, but the influence of dimensionality appears to be consistent
with our empirical observations of approximately $0(n log n)$ performance.

### 2019-02-01 scipy-1.0/paper.tex
Update scipy-1.0/ckdtree.tex
Co-Authored-By: tylerjereddy <tyler.je.reddy@gmail.com>

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{supporting_info/knn_complexity_confirm}
\caption{Assessment of cKDTree nearest neighbor query time complexity as a function of the number of input points (N) along with similar assessment for related algorithms in scikit-learn. The calculations are based on code previously reported\cite{knn-jake}, but updated to use SciPy 1.0.0, Python 3.6, NumPy 1.13.1, and Cython 0.27.3.}
\label{fig:knn-complexity}
\end{figure}
